---
title: "Test Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Test Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Information

This vignette is testing some specific behavior of this package.

```{r setup}
library(AssaySupport)
library(MALDIquant)
```

We will be using the included test data.
Note that this data is from a RapiFlex in linear positive mode. So the resolution is low and the baseline is quite extreme.
```{r load data}
data("test_spectra")
plot(test_spectra[[1]])
```
Next we will preprocess the spectra. 
The included spectra don't actually include an internal standard so we will try to calibrate to an endogenous peak.
```{r preprocess}
prc_IS <- preprocess_spectra(data = test_spectra, 
                              norm_meth = "IS", lockMass = 1807.7, lockMass_tol = 500)
plot(prc_IS[[1]])
```

Next we detect the peaks and convert them to a data.frame.
```{r peakPicking}
peaks <- detectPeaks(prc_IS, method = "SuperSmoother", SNR = 3)
names(peaks) <- names(prc_IS)
peaksdf <- generate_peakdf(peaks)
```

Now we assign IDs to the found masses.
```{r assignIDs}

resdf <- generate_resultdf(peak_df = peaksdf, tol = 500, speciesdf = C99T_commonSpecies)

```